### 2022-11-29 dissertation/chapters/08-results.tex
✨ (final-review): Results Done

The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution. In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.

@@

From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of \index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
            \caption{$\alpha_{0}$ - \acs{SGD}}
            \label{fig:results:case_study:alphas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
            \caption{$\alpha_{6}$ - \acs{Adam}}
            \label{fig:results:case_study:alphas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
            \caption{$\alpha_{7}$ - \acs{PSO}}
            \label{fig:results:case_study:alphas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
            \caption{$\alpha_{8}$ - \acs{GA}}
            \label{fig:results:case_study:alphas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alphas}
\end{figure}

@@

The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals. This interval is defined by the \textit{reanalysis interval} hyper-parameter. The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.

Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used. For all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

@@

Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yield the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, ($c_{1}$), from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth. These variants are denoted as follows. The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.

@@

Figures~\ref{fig:results:reselection:figures:loss:train:car} and ~\ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals. This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.

@@

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
            \caption{Train log loss}
            \label{fig:results:reanalysis:figures:loss:train:mushroom}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
            \caption{Test log loss}
            \label{fig:results:reanalysis:figures:loss:test:mushroom}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
            \caption{Train log accuracy}
            \label{fig:results:reanalysis:figures:accuracy:train:mushroom}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
            \caption{Test log accuracy}
            \label{fig:results:reanalysis:figures:accuracy:test:mushroom}
      \end{subfigure}
      \par\bigskip
      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
      \label{fig:results:reanalysis:figures:mushroom}
\end{figure}

@@

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
            \caption{Train log loss}
            \label{fig:results:reanalysis:figures:loss:train:parkinsons}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
            \caption{Test log loss}
            \label{fig:results:reanalysis:figures:loss:test:parkinsons}
      \end{subfigure}
      \par\bigskip
      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
      \label{fig:results:reanalysis:figures:parkinsons}
\end{figure}

>>>>

The \acs{BHH} does not implement a move-acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution. In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.

@@

From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

@@

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{\index{heuristic}heuristic selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 respectively. Indices 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
            \caption{$\alpha_{0}$ - \acs{SGD}}
            \label{fig:results:case_study:alphas:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
            \caption{$\alpha_{6}$ - \acs{Adam}}
            \label{fig:results:case_study:alphas:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
            \caption{$\alpha_{7}$ - \acs{PSO}}
            \label{fig:results:case_study:alphas:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
            \caption{$\alpha_{8}$ - \acs{GA}}
            \label{fig:results:case_study:alphas:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:alphas}
\end{figure}

@@

The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals. This interval is defined by the \textit{reanalysis interval} hyper-parameter. The reanalysis interval dictates the frequency at which Bayesian analysis is conducted on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.

Notice from Figure~\ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process. Consider a case where all five entities in the entity pool are allocated the same heuristic and that a the replay window size of 10 is used. Then for all ten samples defined in the performance log, $\alpha_{i} = 50$, where $i$ is the index of the $i$-th \index{heuristic}heuristic in the \index{heuristic pool}heuristic pool.

@@

Both the bhh\_baseline (\textcolor{red}{red}) and the bhh\_replay\_250 (\textcolor{green}{green}) configurations make use of the \textit{ibest} credit assignment strategy. The \textit{ibest} credit assignment strategy allocates credit to the heuristic that yields the best performance for the current iteration/step and thus, towards the end of the training process, any random heuristic can yield the best iteration performance. However, since the bhh\_baseline is configured with a small replay window size of 10, and a reanalysis interval of 10, the concentration parameter $\boldsymbol{\alpha}$ is reset to its default value of 1.0 more often than the bhh\_replay\_250 configuration, resulting in a probability distribution that is broader, and thus, explaining the larger variance of $\boldsymbol{\theta}$ throughout.

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
            \caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
            \label{fig:results:case_study:p_HgEC:0:0}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
            \caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
            \label{fig:results:case_study:p_HgEC:0:6}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
            \caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
            \label{fig:results:case_study:p_HgEC:0:7}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
            \caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
            \label{fig:results:case_study:p_HgEC:0:8}
      \end{subfigure}
      \par\bigskip
      \caption{The average calculated proportional posterior \index{heuristic}heuristic selection probabilities for \index{heuristic}heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy. The proportional posterior \index{heuristic}heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
      \label{fig:results:case_study:p_HgEC:0}
\end{figure}

@@

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \index{heuristic pool}\textit{heuristic pool} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. This experimental group utilises the same three variants of the \acs{BHH} as was utilised in Section \ref{sec:results:standalone}, but provides an opportunity to look at the \acs{BHH} \index{heuristic pool}heuristic pool hyper-parameter in more depth. These variants are denoted as follows: The \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics is denoted as \textit{all}, the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics is denoted as \textit{gd}, and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics is denoted as \textit{mh}.

@@

Figures~\ref{fig:results:reselection:figures:loss:train:car} and \ref{fig:results:reselection:figures:loss:train:bike} both show a smooth decline in training loss for all reselection interval configurations of the \acs{BHH}, but larger reselection interval configurations are able to provide better results than lower reselection intervals. This further supports the suggestion that exploitation of low-level \index{heuristic}heuristics is more important than exploration of low-level \index{heuristic}heuristics in this particular case.

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/mushroom.pdf}
            \caption{Train log loss}
            \label{fig:results:reanalysis:figures:loss:train:mushroom}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/mushroom.pdf}
            \caption{Test log loss}
            \label{fig:results:reanalysis:figures:loss:test:mushroom}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/accuracy/mushroom.pdf}
            \caption{Train log accuracy}
            \label{fig:results:reanalysis:figures:accuracy:train:mushroom}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/accuracy/mushroom.pdf}
            \caption{Test log accuracy}
            \label{fig:results:reanalysis:figures:accuracy:test:mushroom}
      \end{subfigure}
      \par\bigskip
      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the mushroom dataset over 30 epochs, illustrated in log scale.}
      \label{fig:results:reanalysis:figures:mushroom}
\end{figure}

@@

\begin{figure}[htb]
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/train/loss/parkinsons.pdf}
            \caption{Train log loss}
            \label{fig:results:reanalysis:figures:loss:train:parkinsons}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{bhh_reanalysis/figures/test/loss/parkinsons.pdf}
            \caption{Test log loss}
            \label{fig:results:reanalysis:figures:loss:test:parkinsons}
      \end{subfigure}
      \par\bigskip
      \caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations for the reanalysis interval hyper-parameter on the parkinsons dataset over 30 epochs, illustrated in log scale.}
      \label{fig:results:reanalysis:figures:parkinsons}
\end{figure}
